---
title: "OTM SG Implementation"
author: "Sean Koh"
date: "22/02/2019"
output: html_document
---
Heavily referenced from David Ten's awesome gist: https://xang1234.github.io/isochrone/

Lib Import:
```{r setup, include<-FALSE}
knitr::opts_chunk$set(echo <- TRUE)
packages = c('tidyverse','leaflet', 'knitr','stringr','httr','geojsonio') 
for (p in packages){
  if(!require(p, character.only = T)){ 
    install.packages(p)
  }
  library(p,character.only = T) 
}
```

This basically tells us what isochrome maps you've already made :
```{r}
list.files("./data/")
```
Here's your method to generate new isochrome maps. Note that we're using a locally hosted instance of Open Trip Planner (OTP), to create our isochrome maps, for more information, please refer to : http://dev.opentripplanner.org/apidoc/1.3.0/ 
    -   It's pretty readable. 
    -   Do note that we're assuming folks would leave at 08:00, but adjust as you'd like; traffic conditions vary with time of day. 
    -   Note walk distance / reluctance setting
    -   The Transfer Time is assumed to be 1 minute only (walk/wait time between transport nodes)
    -   Adjust cut off time in seconds pls tkvm. 
    
```{r}
get_geojson<-function(lat,lng,filename){
    current <- GET(
      "http://localhost:8080/otp/routers/current/isochrone",
      query = list(
        fromPlace = paste(lat,lng,sep = ","), # latlong of place
        mode = "WALK,TRANSIT", # modes we want the route planner to use
        date = "07-10-2018",
        time= "08:00am",
        maxWalkDistance = 1600, # in metres
        walkReluctance = 5,
        minTransferTime = 60, # in secs
        cutoffSec = 900,
        cutoffSec = 1800,
        cutoffSec = 2700,
        cutoffSec = 3600
      )
    )
    
    current <- content(current, as = "text", encoding = "UTF-8")
    write(current, file = paste("./data/",filename,".geojson" , sep = ""))
}
```

We're generating 2 isochrome maps, just to test this.
    -   Changi Airport, T1
    -   SMU 
    
```{r}
get_geojson(1.36173580440684,103.990348825503,
  "Changi-Terminal-1")

get_geojson(1.296568,103.852119,
  "SMU")
```

Read time-travel maps, and generate a leaflet map with what's there.

```{r}
iso <- geojsonio::geojson_read("./data/SMU.geojson",
  what = "sp")

pal=c('cyan','gold','tomato','red')

m<-leaflet(iso) %>%
    setView(lng = 103.8198, lat = 1.3521, zoom = 11) %>%
  addProviderTiles(providers$CartoDB.DarkMatter,
                   options = providerTileOptions(opacity = 0.8))%>%  
  addPolygons(stroke = TRUE, weight=0.5,
              smoothFactor = 0.3, color="black",
              fillOpacity = 0.1,fillColor =pal ) %>%
  addLegend(position="bottomleft",colors=rev(c("lightskyblue","greenyellow","gold","tomato")),
            labels=rev(c("60 min","45 min",
                     "30 min","15 min")),
            opacity = 0.6,
            title="Travel Time with Public Transport")
```

Show map : 

```{r}
m  # Show the map
```

